### 2021-12-17 misc/expo/exotic.tex
Typos

\maketitle{Tsirelson's space\qquad and other exotic constructions}{}{Marcel K. Goh}{16 December 2021}

@@

The field $\RR$ or $\CC$ under the norm given by the absolute value $|\cdot|$ is of course the
simplest Banach space. Other basic examples include the following.
\medskip
\item{i)} Consider an $n$-dimensional vector space over $K$. Writing an element $x$ of this space
as $x = (x_1, \ldots, x_n)$, this vector space can be endowed with the {\it $p$-norm}
$$\norm{x}_p = \Bigl(\sum_{i=1}^n |x_i|^p\Bigr)^{1/p}.$$
for $1\le p<\infty$. This defines a Banach space which we shall denote by $l_p^n$. As $p\to\infty$,
this approaches the {\it maximum norm}
$$\norm{x}_\infty = \max_{1\le i\le n} |x_i|,$$
and we denote this Banach space by $l_\infty^n$.
\smallskip
\item{ii)} For $1\le p< \infty$, the $p$-norm for infinite sequences $x = (x_n)_{n=1}^\infty$ is given by
$$\norm{x}_{l_p} = \Bigl(\sum_{i=1}^\infty |x_i|^p \Bigr)^{1/p}.$$
As $p\to\infty$, this approaches the {\it supremum norm}
$$\norm{x}_{l_\infty} = \sup_{i\ge 1} |x_i|.$$
For $1\le p\le \infty$, the set $l_p$ of all infinite sequences $x$ with $\norm{x}{l_p}$ finite is a Banach space;
when $p=\infty$, these are the bounded sequences.
\smallskip
\item{iii)} Let $c_0$ be the normed vector subspace of $l_\infty$ consisting of sequences that tend to zero.
It can be shown that this subspace is closed and thus itself a Banach space.
\medskip
The latter two examples are infinite-dimensional, meaning that in these cases one can exhibit an
infinite sequence of vectors that are all linearly independent.

@@

\proof Suppose that $\{e_1\}_{i=1}^\infty$ is a countable Hamel basis for $X$. For integers $n\ge 1$,
let $X_n$ denote the linear span of $\{e_1,\ldots,e_n\}$. Each normed vector space $X_n$ is finite-dimensional
and thus complete, which implies that each $X_n$ is closed in $X$. We now show that every $X_n$ has empty
interior, which completes the proof.\slug

>>>>

\maketitle{Tsirelson's space and other exotic constructions}{}{Marcel K. Goh}{16 December 2021}

@@

The field $\RR$ or $\CC$ under the norm given by the absolute value $|\cdot|$ is of course the
simplest Banach space. Other basic examples include the following.
\medskip
\item{i)} Consider an $n$-dimensional vector space over $K$. Writing an element $x$ of this space
as $x = (x_1, \ldots, x_n)$, this vector space can be endowed with the {\it $p$-norm}
$$\norm{x}_p = \Bigl(\sum_{i=1}^n |x_i|^p\Bigr)^{1/p}.$$
for $1\le p<\infty$. This defines a Banach space which we shall denote by $l_p^n$. As $p\to\infty$,
this approaches the {\it maximum norm}
$$\norm{x}_\infty = \max_{1\le i\le n} |x_i|,$$
and we denote this Banach space by $l_\infty^n$.
\smallskip
\item{ii)} For $1\le p< \infty$, the $p$-norm for infinite sequences $x = (x_n)_{n=1}^\infty$ is given by
$$\norm{x}_{l_p} = \Bigl(\sum_{i=1}^\infty |x_i|^p \Bigr)^{1/p}.$$
As $p\to\infty$, this approaches the {\it supremum norm}
$$\norm{x}_{l_\infty} = \sup_{i\ge 1} |x_i|.$$
For $1\le p\le \infty$, the set $l_p$ of all infinite sequences $x$ with $\norm{x}_{l_p}$ finite is a Banach space;
when $p=\infty$, these are the bounded sequences.
\smallskip
\item{iii)} Let $c_0$ be the normed vector subspace of $l_\infty$ consisting of sequences that tend to zero.
It can be shown that this subspace is closed and thus itself a Banach space.
\medskip
The latter two examples are infinite-dimensional, meaning that in these cases one can exhibit an
infinite sequence of vectors that are all linearly independent.

@@

\proof Suppose that $\{e_1\}_{i=1}^\infty$ is a countable Hamel basis for $X$. For integers $n\ge 1$,
let $X_n$ denote the linear span of $\{e_1,\ldots,e_n\}$. Each normed vector space $X_n$ is finite-dimensional
and thus complete, which implies that each $X_n$ is closed in $X$. But each of these subspaces is proper,
so by the lemma above, so all of these subspaces have empty interior, which contradicts the Baire category
theorem.\slug
